Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-20 paper/paper.tex
Fix the whole introduction paragraph

In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
questions in this paper (Section \ref{correlations}):
\begin{itemize}
  \item does the presence of attachments and their type (e.g. code snippet, screenshot) influence the \emph{Time-To-Close} for 
  a ticket?
  \item does the presence of stack traces improve the ticket quality?
  \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
  \item is there a relationship between the number of comments influence \emph{Time-To-Close}?
  \item is there a relationship between 
\end{itemize}

This study brings several contributions to the research community:
\begin{itemize}
  \item an innovative tool was built for the purpose of this project, its strengths lying in its simplicity, speed and
  extensability;
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000)
  extracted from 38 different projects;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

In Section \ref{related_work} we iterate over state-of-the art studies in the field and then continue with 
Section \ref{building} where we discuss how the ticket data set was collected and analysed. We continue with describing 
the data set (Section \ref{characterising}) where we provide insights into various aspects of the data (e.g. size of database,
number of tickets with attachments) and then discuss about correlations between the variables (Section \ref{correlations}).
Finally, we provide future research directions in Section \ref{future_work} and present our conclusions in Section \ref{conclusions}.

>>>>

In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
questions in this paper (Section \ref{correlations}):
\begin{itemize}
  \item does the presence of attachments and their type (e.g. code snippet, screenshot) influence the \emph{Time-To-Close} for 
  a ticket?
  \item does the presence of stack traces improve the ticket quality?
  \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
  \item is there a relationship between the number of words in comments and \emph{Time-To-Close}?
  \item does the total number of words in summary and description have an impact on \emph{Time-To-Close}?
  \item does the number of grammar errors in summary, description and comments have an effect on the quality of a ticket?
  \item does a positive or negative ticket influence its \emph{Time-To-Close}?
\end{itemize}

This study brings several contributions to the research community:
\begin{itemize}
  \item an innovative tool was built for the purpose of this project, providing efficient data collection and analysis of
  tickets;
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000)
  extracted from 38 different projects;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

The rest of the paper is structured as follows. In Section \ref{related_work} we iterate over state-of-the art studies in 
the field and then continue with Section \ref{building} where we discuss how the ticket data set was collected and 
analysed. We continue with describing the data set (Section \ref{characterising}) where we provide insights into various 
aspects of the data (e.g. size of database, number of tickets with attachments) and then discuss correlations between 
the variables (Section \ref{correlations}). Finally, we provide future research directions in Section \ref{future_work} 
and present our conclusions in Section \ref{conclusions}.
